%-------------------------------------------------------------
%----------TECHNICAL REPORTS-------------------
%-------------------------------------------------------------
\vspace{-0.1in}   
\sectiontitle{Technical\\Reports\\ \color{blue}\href{https://ui.adsabs.harvard.edu/public-libraries/QCbOxuv6T6GmSVRgbdxYiw}{(ADS link)}\color{black}}
\begin{revnumerate}[24]
\item{\textsc{Summary of the COS Cycle 22 Calibration Program}\\
Sonnentrucker; P.; Becker, G.; {\bf Bostroem, K. A.}; Debes, J.H.; Ely, J.; Fox, A.; Lockwood, S.; Oliveira, C.; Penton, S.; Proffitt, C.; Roman-Duval, J.; Sahnow, D.; Sana, H.; Taylor, J.; Welty, A. D.; Wheeler, T., 2016, Tech. rep 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2016cos..rept....3S/abstract}{(ADS link)}\color{black}}\\ %ISR
%\\
\item{\textsc{Summary of the COS Cycle 21 Calibration Program}\\
Sana, H.; Roman-Duval, J.; Ely, J.; {\bf Bostroem, K. A.}; Lockwood, S.; Oliveira, C.; Penton, S.; Proffitt, C.; Sahnow, D.; Sonnentrucker, P.; Welty, A. D.; Wheeler, T., 2015, Tech. rep 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2015cos..rept....6S/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{Changes to the COS Extraction Algorithm for Lifetime Position 3}\\
Proffitt, C. R.; {\bf Bostroem, K. A.}; Ely, J.; Foster, D.; Hernandez, S.; Hodge, P.; Jedrzejewski, R. I.; Lockwood, S. A.; Massa, D.; Peeples, M. S.; Oliveira, C. M.; Penton, S. V.; Plesha, R.; Roman-Duval, J.; Sana, H.; Sahnow, D. J.; Sonnentrucker, P.; Taylor, J. M.,  2015, Tech. rep 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2015cos..rept....3P/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{Summary of the COS Cycle 20 Calibration Program}\\
Roman-Duval, J.; Aloisi, A.; {\bf Bostroem, K. A.}; Ely, J.; Holland, S.; Lockwood, S.; Oliveira, C.; Penton, S.; Proffitt, C.; Sahnow, D.; Sonnentrucker, P.; Welty, A. D.; Wheeler, T., 2015, Tech. rep 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2015cos..rept....2R/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{The Time-Dependent Sensitivity of the MAMA and CCD Long-Slit Gratings}\\
Holland, S. T.; Aloisi, A.; {\bf Bostroem, K. A.}; Oliveria, C.; Proffitt, C.,  2014, Tech. rep 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2014stis.rept....2H/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{Summary of the STIS Cycle 19 Calibration Program}\\
Roman-Duval, J.; Ely, J.; Aloisi, A.; Oliveira, C.; Proffitt, C.; Hernandez, S.; Mason, E.; Sonnetrucker, P.; Wolfe, M.; Long, C.; DiFelice, A.; \textbf{Bostroem, K. A.}; Holland, S.; Lockwood, S.; Cox, C.; Wheeler, T., 2014, Tech. rep 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2014stis.rept....1R/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{Summary of the Cycle 19 COS Calibration Program}\\
Roman-Duval, J.; Ely, J.; Oliveira, C.; Proffitt, C.; Aloisi, A.; \textbf{Bostroem, K. A.}; Cox, C.; Lockwood, S.; Mason, E.; Massa, D.; Osten, R.; Penton, S.; Sahnow, D.; Sonnetrucker, P.; Wheeler, T., 2014, Tech. rep 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2014cos..rept....1R/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{Updated Absolute Flux Calibration of the COS FUV Modes}\\
Massa, D.; Ely, J.; Osten, R.; Penton, S.; Aloisi, A.; \textbf{Bostroem, K. A.}; Roman-Duval, J.; Proffitt, C. 2014, Tech. rep. 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2014cos..rept....9M/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{Summary of STIS Cycle 18 Calibration Program}\\
Kriss, G. A.; Wolfe, M. A.; Aloisi, A.; \textbf{Bostroem, K. A.}; Cox, C.; Dixon, V.; Ely, J.; Long, C.; Mason, E.; Massa, D.; Osten, R.; Proffitt, C.; Roman-Duval, J.; Sonnentrucker, P.; Wheeler, T.; Zheng, W., 2013, Tech. rep. 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2013stis.rept....3K/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{Summary of Results from the First Move to a New COS FUV Lifetime Position}\\
Osten, R. A.; Aloisi, A.; \textbf{Bostroem, K. A.};  Debes, J.; Ely, J.; Hodge, P. E.; Kriss, G.; Massa, D.; Oliveira, C.; Osten, R.; Osterman, S. N.; Penton, S. V.; Proffitt, C.; Roman-Duval, J.; Sonnentrucker, P., 2013, Tech. rep. 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2013cos..rept...16O/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{Characterization, modeling, and management of the COS FUV detector lifetime}\\
Sahnow, D. J.; Aloisi, A.; \textbf{Bostroem, K. A.}; Debes, J.; Ely, J.; Hodge, P. E.; Kriss, G.; Massa, D.; Oliveira, C.; Osten, R.; Osterman, S. N.; Penton, S. V.; Proffitt, C.; Roman-Duval, J.; Sonnentrucker, P., 2013, Proc. of the SPIE, 8859 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2013SPIE.8859E..0SS/abstract}{(ADS link)}\color{black}}\\

\item{\textsc{Summary of the COS Cycle 18 Calibration Program}\\
Kriss, G. A.; Wolfe, M.; Aloisi, A.; \textbf{Bostroem, K. A.}; Cox, C.; Ely, J.; Long, C.; Massa, D.; Oliveria, C.; Osten, R.; Proffitt, C.; Sahnow, D.; Wheeler, T.; Zheng, W., 2013, Tech. rep. 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2013cos..rept....4K/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{Second COS FUV Lifetime Position Results from the Focus Sweep Enabling Program}\\
Oliveira, C.; \textbf{Bostroem, K. A.}; Osterman, S., FENA3 (12796), 2013, Tech. rep. 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2013cos..rept....1O/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{Summary of the COS Cycle 17 Calibration Program}\\
Osten, R. A.; Wolfe, M.; Ake, T.; Aloisi, A.; \textbf{Bostroem, K. A.}; Dixon, W. V. D.; Ghavamian, P.; Goudfrooij, P.; Ely, J.; Massa, D.; Niemi, S.; Oliveira, C.; Osterman, S.; Pascucci, I.; Penton, S.; Proffitt, C.; Sahnow, D.; Wheeler, T.; York, B.; Zheng, W., 2012, Tech. rep. 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2012cos..rept....2O/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{Post-SM4 Sensitivity Calibration of the STIS Echelle Modes}\\
{\bf Bostroem, K. A.}; Aloisi, A.; Bohlin, R.; Hodge, P.; Proffitt, C., 2012, Tech. rep 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2012stis.rept....1B/abstract}{(ADS link)}\color{black}}\\%Post-SM4 Sensitivity Calibration of the STIS Echelle Modes

\item{\textsc{The COS FUV channel: on-orbit performance trends and early characterization of a new detector lifetime position}\\
Sahnow, D. J.; Aloisi, A.; \textbf{Bostroem, K. A.}; Debes, J.; Duval, J.; Ely, J.; Hodge, P. E.; Kriss, G.; Lindsay, K.; Massa, D.; Oliveira, C.; Osten, R.; Osterman, S. N.; Penton, S. V.; Proffitt, C.; Sonnentrucker, P.; York, B., 2012, Proc. of the SPIE, 8443 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2012SPIE.8443E..4CS/abstract}{(ADS link)}\color{black}}\\

\item{\textsc{Summary of the STIS Cycle 17 Calibration Program}\\
Wolfe, M. A.; Osten, R. A.; Hernandez, S.; Aloisi, A.; Bohlin, R.; \textbf{Bostroem, K. A.}; Diaz, R.; Dixon, V.; Ely, J.; Hodge, P.; Lennon, D.; Mason, E.; Niemi, S.; Pascuucci, I.; Proffitt, C.; Wheeler, T.; Zheng, W., 2012, Tech. rep. 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2012stis.rept....3W/abstract}{(ADS link)}\color{black}}\\%ISR

\item{\textsc{Gain sag in the FUV detector of the Cosmic Origins Spectrograph}\\
Sahnow, D. J.; Oliveira, C.; Aloisi, A.; Hodge, P. E.; Massa, D.; Osten, R.; Proffitt, C.; \textbf{Bostroem, K. A.}; McPhate, J. B.; B\'{e}land, S.; Osterman, S. N.; Penton, S. V., 2011,  Proc. of the SPIE, 8145 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2011SPIE.8145E..0QS/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{Updated Results from the COS Spectroscopic Sensitivity Monitoring Program}\\
Osten, R. A.; Massa, D.; \textbf{Bostroem, K. A.}; Aloisi, A.; Proffitt, C., 2011, Tech. rep. 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2011cos..rept....2O/abstract}{(ADS link)}\color{black}}\\ %ISR

\item{\textsc{STIS Data Handbook v. 6.0}\\
{\bf Bostroem, K. A.} \& Proffitt, C. 2011
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2011stis.book.....B/abstract}{(ADS link)}\color{black}}\\

\item{\textsc{Post - SM4 Flux Calibration of the STIS Echelle Modes}\\
\textbf{Bostroem, K. A.}; Aloisi, A.; Bohlin, R. C.; Proffitt, C. R.; Osten, R. A.; Lennon, D., 2010, HST Calibration Workshop Proceedings
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2010hstc.workE..51B/abstract}{(ADS link)}\color{black}}\\%Post - SM4 Flux Calibration of the STIS Echelle Modes

\item{\textsc{Trend of Dark Rates of the COS and STIS NUV MAMA Detectors}\\
Zheng, W.; Proffitt, C. R.; Sahnow, D.; Ake, T. B.; Keyes, C.; Goudfrooij, P.; Hodge, P.; Oliveira, C.; \textbf{Bostroem, K. A.}; Long, C.; Aloisi, A., 2010, HST Calibration Workshop Proceedings 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2010hstc.workE..47Z/abstract}{(ADS link)}\color{black}}\\

\item{\textsc{Performance of the Space Telescope Imaging Spectrograph after SM4}\\
Proffitt, C. R.; Aloisi, A.; Bohlin, C.; \textbf{Bostroem, K. A.}; Cox, C. R.; Diaz, R. I.; Dixon, W. V.; Goudfrooij, P.; Hodge, P.; Kaiser, M. E.; Lallo, M. D.; Lennon, D.; Niemi, S.; Osten, R. A.; Pascucci, I.; Smith, E.; Wolfe, M. A.; York, B.; Zheng, W.; Gull, T. R.; Lindler, D. J.; Woodgate, B. E., 2010, HST Calibration Workshop Proceedings
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2010hstc.workE...6P/abstract}{(ADS link)}\color{black}}\\
%\\
\item{\textsc{The On-Orbit Performance of the Cosmic Origins Spectrograph}\\
Aloisi, A.; Ake, T.; \textbf{Bostroem, K. A.}; Bohlin, R.; Cox, C.; Diaz, R.; Dixon, V.; Ghavamian, P.; Goudfrooij, P.; Hartig, G.; Hodge, P.; Keyes, C.; Kriss, G.; Lallo, M.; Lennon, D.; Massa, D.; Niemi, S.; Oliveira, C.; Osten, R.; Proffitt, C. R.; Sahnow, D.; Smith, E.; Wheeler, T.; Wolfe, M.; York, B.; Zheng, W.; Green, J.; Froning, C.; Beland, S.; Burgh, E.; France, K.; Osterman, S.; Penton, S.; McPhate, J.; Delker, T., 2010, HST Calibration Workshop Proceedings 
\color{blue}\href{https://ui.adsabs.harvard.edu/abs/2010hstc.workE...3A/abstract}{(ADS link)}\color{black}}\\
\end{revnumerate}
%16 technical reports with {\bf Bostroem} as co-author; see \color{blue}\url{http://bit.ly/2iUeoax }\color{black}\hspace*{0pt} for details
